Download final data

### 2023-05-05 analysis/data-final.qmd
Add targets as dependencies

>>>>

```{r include=FALSE}
# Add these final data files as targets dependencies
library(targets)
tar_load(c(data_daily_stata, data_daily_csv, data_daily_rds,
           data_weekly_stata, data_weekly_csv, data_weekly_rds))
tar_load(c(data_daily_stata_website, data_daily_csv_website, data_daily_rds_website,
           data_weekly_stata_website, data_weekly_csv_website, data_weekly_rds_website))
```
